Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-21 Papers/ms.tex
Three new references

\section{Finding dark substructures}
If possible, it is best
If we are interested in detecting and measuring the properties of
possible dark substructures in a lens galaxy,
a superposition of an unknown number of ``blobs'' is the
most natural model. In addition, if we want to constrain the mass function of
these blobs \citep[e.g.][]{2009MNRAS.400.1583V, 2014MNRAS.442.2017V},
we will need a hierarchical model which specifies the prior probability
distribution for the masses conditional on some hyperparameters. Inferring the
mass function of the blobs then reduces to calculating the posterior
distribution for the hyperparameters.

@@

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford) and Tommaso Treu (UCLA)
for valuable discussion.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Birrer, Amara, 
\& Refregier}{2015}]{2015arXiv150407629B} Birrer S., Amara A., Refregier A., 2015, arXiv, arXiv:1504.07629

@@

>>>>

\section{Finding dark substructures}
If possible, it is best
If we are interested in detecting and measuring the properties of
possible dark substructures in a lens galaxy,
a superposition of an unknown number of ``blobs'' is the
most natural model. In addition, if we want to constrain the mass function of
these blobs \citep[e.g.][]{2009MNRAS.400.1583V, 2014MNRAS.442.2017V},
we will need a hierarchical model which specifies the prior probability
distribution for the masses conditional on some hyperparameters. Inferring the
mass function of the blobs then reduces to calculating the posterior
distribution for the hyperparameters. This is related to the general principle
that we should (ideally) construct our inference methods so that the
quantities we infer directly answer our scientific questions
\citep{2015arXiv150507840A, 2015ApJ...807...87S, pancoast}.

@@

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
Ross Fadely (NYU), and Alan Heavens (Edinburgh)
for valuable discussion.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Alsing et al.}{2015}]{2015arXiv150507840A} 
Alsing J., Heavens A., Jaffe A.~H., Kiessling A., Wandelt B., Hoffmann T., 
2015, arXiv, arXiv:1505.07840

\bibitem[\protect\citeauthoryear{Birrer, Amara, 
\& Refregier}{2015}]{2015arXiv150407629B} Birrer S., Amara A., Refregier A., 2015, arXiv, arXiv:1504.07629

@@

\bibitem[\protect\citeauthoryear{Pancoast, Brewer, 
\& Treu}{2011}]{pancoast} Pancoast A., Brewer B.~J., Treu T., 2011, ApJ, 730, 139

\bibitem[\protect\citeauthoryear{Schneider et 
al.}{2015}]{2015ApJ...807...87S} Schneider M.~D., Hogg D.~W., Marshall 
P.~J., Dawson W.~A., Meyers J., Bard D.~J., Lang D., 2015, ApJ, 807, 87
